---
output:
  html_document:
    df_print: paged
css: ashlin_style.css
---
<head><style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:HoneyDew;
    	cursor: url('/Users/zoeervolino/Documents/zoe/SocialStudies/Strawberry normal select.cur'), default;
}
<meta name="viewport" content="width=device-width, initial-scale=1" /> 
</head></style>

<p style="text-align:left">
<small><small>Zoe Morales Ervolino 
<br>
(she / her / ella)
<br>
4.29.21</small></small></p>

<hr>

<b>Welcome back to ELA!</b>

<h1>ASHLINISMS</h1>
 
Some "Ashlinisms" include: 
<small><br>
- "marginalia"
<br>
- "consternation"
<br>
- "SORE-ee" instead of "sorry"</small>
<br>

<small>That was fun! Now, let's take a step back to review some basics about how we can strengthen our writing.</small>

<hr>

```{r image1, echo=FALSE, out.width="80%", fig.align='center'}

brain <- "/Users/zoeervolino/Documents/zoe/SocialStudies/Expanding-Brain.jpeg"
knitr::include_graphics(brain)

```
<hr>

<h2>TAG</h2>
```{r image2, echo=FALSE, out.width="20%", fig.align='center'}

tag <- "/Users/zoeervolino/Documents/zoe/SocialStudies/tag.jpeg"
knitr::include_graphics(tag)

```
<h3>(you're it!)</h3>

<b>T- Title

A - Author

G - Genre**</b>
<br>
<h3>for example:</h3>

<h4><br>
A timeless reckoning with jealousy, fidelity, and love, William Shakespeare's comedic play, <i>A Midsummer Night's Dream</i> highlights the absurd qualities of the human experience.
<br>
<i><small>**REMINDER: don't forget how to properly cite different <u>types</u> of texts. For the purpose of this class we will use MLA but Chicago is widely used in historical writing and APA is used in scientific literature</i></small></h4>
<br>

<h3>CITATION examples:</h3>
<h4> 

- An 1861 article titled, "Othello's Shadow," argued that the Shakespearean work presented a case for abolition of enslaved Africans.
  
  
- As a widely acclaimed novel highlighting class disparities in 1920s New York, <i>The Great Gatsby</i> transformed the American literary  cannon.
  
  
- William Carlos Williams' poem, "The Red Wheelbarrow," invites the reader to reconsider the simple pleasures of quotidian living.
  
  
- Broadcasted on American television during the 1990s, <u>The Fresh Prince of Bel-Air</u> managed to effectively refute a static representation of blackness in media.</h4>

<hr>

<h2>BLT</h2>
```{r image3, echo=FALSE, out.width="20%", fig.align='center'}

blt <- "/Users/zoeervolino/Documents/zoe/SocialStudies/27Diaryrex4-articleLarge.jpeg"
knitr::include_graphics(blt)

```
<h3>(no, in this case you CAN'T hold the 'B' even if you're vegan)</h3>
<br>
<b>B - Background

L - Location

T - Time</b>

<h3>for example:</h3>

<h4>- First performed around 1596, Shakespeare's <i>A Midsummer Night's Dream</i> traces the escapades of four Athenians who escape to the forest only to find themselves bewitched by supernatural forces.</h4>

<hr>

<h2>SQUID</h2>
```{r image4, echo=FALSE, out.width="20%", fig.align='center'}

squid <- "/Users/zoeervolino/Documents/zoe/SocialStudies/squid.jpeg"
knitr::include_graphics(squid)

```
<br>
<b>SQ - Select a Quotation

U - Understand

I - Identify 

D - Demonstrate Significance</b>

<h3>for example:</h3>

Select a Quotation: 
<h4><small>- "As if our hands, our sides, voices, and minds /
Had been incorporate. So we grew together /
Like to a double cherry, seeming parted, /
But yet an union in partition, /
Two lovely berries molded on one stem..." (A Midsummer Night's Dream, 3.2, 97)</small></h4>

Understand: 
<h4>Helena employs the analogy of a double cherry to describe the intimate relationship she shares with Hermia, and, in particular, to simultaneously highlight their shared formation as well as their individuality.</h4> 

Identify: <h4>This metaphor works in context to emphasize the betrayal that Helena feels in having her lover suddenly turn his attention towards her lifelong friend.</h4>

Demonstrate Signficance: <h4>In comparing Hermia and Helena's relationship to that of "[t]wo lovely berries molded on one stem," Shakespeare highlights how the womens' friendship occupies a unique position oscillating between one conjoined entity and two individual beings.

<br>This rhetorical construction underscores the betrayal that Helena feels upon discovering that her former lover has redirected his affections towards Hermia.</h4>

***

<hr>



