---
output:
  html_document:
    df_print: paged
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'Ashlinisms.html'))})
css: ashlin_style.css
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:HoneyDew;
    	cursor: url('/Users/zoeervolino/Documents/zoe/SocialStudiesNew/Strawberry normal select.cur'), default;
}
</style>

<p style="text-align:left">
<small><small>Zoe Morales Ervolino 
<br>
(she / her / ella)
<br>
4.29.21</small></small></p>

<hr>

<h1>ASHLINISMS</h1>

<b>Welcome back to ELA!</b>

<a href="intro.html"><center><i><h3>ELA INTRO</i><h3></center></a>
<br>
<a href="squid.html"><center><i><h3>ELA SQUID</i><h3></center></a>

 
Some "Ashlinisms" include: 
<br>
- "marginalia"
<br>
- "consternation"
<br>
- "take a fiver"
<br>
- "SORE-ee" instead of "sorry"
<br>
<br>
That was fun! Now, let's take a step back to review some basics about how we can strengthen our writing.

<hr>

```{r image1, echo=FALSE, out.width="40%", fig.align='center'}

brain <- "/Users/zoeervolino/Documents/zoe/SocialStudiesNew/Expanding-Brain.jpeg"
knitr::include_graphics(brain)

```
<hr>

<h2>TAG</h2>
```{r image2, echo=FALSE, out.width="20%", fig.align='center'}

tag <- "/Users/zoeervolino/Documents/zoe/SocialStudiesNew/tag.jpeg"
knitr::include_graphics(tag)

```
<center>
<h3>(you're it!)</h3>
</center>
<center>
<b>T - Title
</center>
<center>
A - Author
</center>
<center>
G - Genre**</b>
</center>

<br>
<h3>for example:</h3>

<h4><br>
A timeless reckoning with jealousy, fidelity, and love, William Shakespeare's comedic play, <i>A Midsummer Night's Dream</i>, highlights the absurd qualities of the human experience.
<br>
<i><small>**REMINDER: don't forget how to properly cite different <u>types</u> of texts. For the purpose of this class we will use MLA but Chicago is widely used in historical writing and APA is used in scientific literature.</i></small></h4>

<br>
<br>
<h3>CITATION examples:</h3>
<h4> 
  - An 1861 article titled, "Othello's Shadow," argued that the Shakespearean work presented a case for abolition of enslaved Africans.
  
  
  - As a widely acclaimed novel highlighting class disparities in 1920s New York, <i>The Great Gatsby</i> transformed the American literary  cannon.
  
  
  - William Carlos Williams' poem, "The Red Wheelbarrow," invites the reader to reconsider the foundations of daily life.
  
  
  - Broadcasted on American television during the 1990s, <u>The Fresh Prince of Bel-Air</u> managed to effectively refute a static representation of blackness in media.</h4>

<hr>

<h2>BLT</h2>
```{r image3, echo=FALSE, out.width="20%", fig.align='center'}

blt <- "/Users/zoeervolino/Documents/zoe/SocialStudiesNew/27Diaryrex4-articleLarge.jpeg"
knitr::include_graphics(blt)

```
<h3>(no, in this case you CAN'T hold the 'B' even if you're vegan)</h3>
<br>
<center>
<b>B - Background
</center>
<center>
L - Location
</center>
<center>
T - Time</b>
</center>
<center>
<h3>for example:</h3>
</center>
<center>
<h4>- First performed around 1596, Shakespeare's <i>A Midsummer Night's Dream</i> traces the escapades of four Athenians who escape to the forest only to find themselves bewitched by supernatural forces.</h4>
</center>
<hr>
<br>


