---
output:
  html_document:
    df_print: paged
    
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'squid.html'))})
 
css: ashlin_style.css
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:HoneyDew;
    	cursor: url('/Users/zoeervolino/Documents/zoe/SocialStudiesNew/Strawberry normal select.cur'), default;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

<p style="text-align:left">
<small><small>Zoe Morales Ervolino 
<br>
(she / her / ella)
<br>
05.03.21</small></small></p>

<h5><b>Welcome back to ELA!</b></h5>
<br>

<h2>SQUID</h2>
```{r image4, echo=FALSE, out.width="20%", fig.align='center'}

squid <- "/Users/zoeervolino/Documents/zoe/SocialStudiesNew/squid.jpeg"
knitr::include_graphics(squid)

```
<br>
<b>SQ - Select a Quotation

U - Understand

I - Identify 

D - Demonstrate Significance</b>
<br>

<h5>for example:</h5>
<br>
<h3>Select a Quotation:</h3>
<h4>- "As if our hands, our sides, voices, and minds /
Had been incorporate. So we grew together /
Like to a double cherry, seeming parted, /
But yet an union in partition, /
Two lovely berries molded on one stem..." (A Midsummer Night's Dream, 3.2, 97)</h4>
<br>

<h3>Understand:</h3>
<h4>Helena employs the analogy of a double cherry to describe the intimate relationship she shares with Hermia, and, in doing so, simultaneously highlights the shared experience of the two, in addition to their individuality.</h4> 
<br>
<h3>Identify:</h3> 
<h4>This metaphor works in context to emphasize the betrayal that Helena feels in having her lover suddenly turn his attention towards her lifelong friend.</h4>
<br>

<h3>Demonstrate Signficance:</h3> 
<h4>In comparing Hermia and Helena's relationship to that of "[t]wo lovely berries molded on one stem," Shakespeare highlights how the womens' friendship occupies a unique position that oscillates between one conjoined entity and two individual beings.
This rhetorical construction underscores the betrayal that Helena feels upon discovering that her former lover has redirected his affections towards Hermia.</h4>

***

<hr>



