---
output:
  html_document:
    df_print: paged
  pdf_document: default
css: ashlin_style.css
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:HoneyDew;
    	cursor: url('/Users/zoeervolino/Documents/zoe/SocialStudies/Strawberry normal select.cur'), default;
}
</style>

<p style="text-align:left">
<small><small>Zoe Morales Ervolino 
<br>
(she / her / ella)
<br>
4.29.21</small></small></p>

<hr>
<center><h1>ELA</h1></center>

<b>Welcome back to ELA!</b><br>In this lesson, we will review the components that form <u>a strong introductory paragraph</u> for a literary essay.

<i>This is a test.</i> 

<br>
<br>

<h3>Structure of a successful introduction:</h3>

<h4>1. <b>Hook</b>: grabs the reader's attention
<br>

<h4>2. <b>TAG</b>: Title, Author, Genre
<br>

<h4>3. <b>BLT</b>: Background, Location, Time
<br>

<h4>4. <b>Synopsis</b>: a birds eye view of the world
<br>

<h4>5. <b>Focus</b>: narrowing in to set up the topic
<br>

<h4>6. <b>Thesis</b>: a strong claim supported by evidence from the text
<br>
</h4>
<br>

```{r image1, echo=FALSE, out.width="40%", fig.align='center'}

##brain <- "/Users/zoeervolino/Documents/zoe/SocialStudies/Expanding-Brain.jpeg"
##knitr::include_graphics(brain)

```
<hr>

<h2>TAG</h2>
```{r image2, echo=FALSE, out.width="20%", fig.align='center'}

tag <- "/Users/zoeervolino/Documents/zoe/SocialStudies/tag.jpeg"
knitr::include_graphics(tag)

```
<h3>(you're it!)</h3>

<b>T - Title

A - Author

G - Genre**</b>
<br>
<br>

<h3>for example:</h3>

<h4><br>
A timeless reckoning with jealousy, fidelity, and love, William Shakespeare's comedic play, <i>A Midsummer Night's Dream</i>, highlights the absurd qualities of the human experience.
<br>
<br>
<i><small>**REMINDER: don't forget how to properly cite different <u>types</u> of texts. For the purpose of this class we will use MLA but Chicago is widely used in historical writing and APA is used in scientific literature.</i></small></h4>
<br>
<hr>

<h2>BLT</h2>
```{r image3, echo=FALSE, out.width="20%", fig.align='center'}

blt <- "/Users/zoeervolino/Documents/zoe/SocialStudies/27Diaryrex4-articleLarge.jpeg"
knitr::include_graphics(blt)

```
<h3>(no, in this case you CAN'T hold the 'B' even if you're vegan)</h3>
<br>

<b>B - Background

L - Location

T - Time</b>
<br>
<h3>for example:</h3>

<h4>First performed around 1596, Shakespeare's <i>A Midsummer Night's Dream</i> traces the escapades of four Athenians who retreat to the forest only to find themselves bewitched by supernatural forces.</h4>

<hr>
<br>
<br>

<h4><b>Synopsis<br></b>
Provides relevant insight into the world of the text to provide a foundation for the argument to come (thesis)
<br>

<b>Focus<br></b>
A transitional sentence or two that places a "viewfinder" on the broader text and defines the area of interest that you intend to discuss in the essay.

What's a viewfinder? The camera component that shows the photographer the area of the subject that will be included in a photograph.
<br>

<>Thesis<br></b>
1. Makes an argumentative assertion<br>
2. Provides a roadmap for how you will prove your claim<br>
</h4>
<br>

<h3>for example:</h3>

[insert example]

