---
output:
  html_document:
    df_print: paged
  pdf_document: default

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'intro.html'))})
 
css: ashlin_style.css
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:HoneyDew;
    	cursor: url('/Users/zoeervolino/Documents/zoe/SocialStudiesNew/Strawberry normal select.cur'), default;
}
</style>

<center><h1>ELA</h1></center>

<b>Welcome back to ELA!</b><br>In this lesson, we will review the components that form <u>a strong introductory paragraph</u> for a literary essay.
<br>

<center>
<h3>Structure of a successful introduction:</h3>

<h4>1. <b>Hook</b>: grabs the reader's attention
<br>

<h4>2. <b>TAG</b>: Title, Author, Genre
<br>

<h4>3. <b>BLT</b>: Background, Location, Time
<br>

<h4>4. <b>Synopsis</b>: a birds eye view of the world
<br>

<h4>5. <b>Focus</b>: narrowing in to set up the topic
<br>

<h4>6. <b>Thesis</b>: a strong claim supported by evidence from the text
<br>
</h4>
<br>
</center>

```{r image1, echo=FALSE, out.width="40%", fig.align='center'}

##brain <- "/Users/zoeervolino/Documents/zoe/SocialStudiesNew/Expanding-Brain.jpeg"
##knitr::include_graphics(brain)

```
<hr>

<center>
<h2>TAG</h2>
</center>
```{r image2, echo=FALSE, out.width="20%", fig.align='center'}

tag <- "/Users/zoeervolino/Documents/zoe/SocialStudiesNew/tag.jpeg"
knitr::include_graphics(tag)

```
<h3>(you're it!)</h3>

<center>

<b>
<center>T - Title</center>

<center>A - Author</center>

<center>G - Genre**</center></b>
<br>
<br>
</center>

<h3>for example:</h3>

<h4><br>
<center>
A timeless reckoning with jealousy, fidelity, and love, William Shakespeare's comedic play, <i>A Midsummer Night's Dream</i>, highlights the absurd qualities of the human experience.
</center>

<br>
<br>

<center>
<i><small>**REMINDER: don't forget how to properly cite different <u>types</u> of texts. For the purpose of this class we will use MLA but Chicago is widely used in historical writing and APA is used in scientific literature.</i></small></h4>
</center>

<br>
<hr>

<center>
<h2>BLT</h2>
</center>
```{r image3, echo=FALSE, out.width="20%", fig.align='center'}

blt <- "/Users/zoeervolino/Documents/zoe/SocialStudiesNew/27Diaryrex4-articleLarge.jpeg"
knitr::include_graphics(blt)

```
<center>
<h3>(no, in this case you CAN'T hold the 'B' even if you're vegan)</h3>
<br>
</center>



<b>
<center>B - Background</center>


<center>L - Location</center>

<center>T - Time</center>
</b>

<br>
<center>
<h3>for example:</h3>
</center>

<center>

<h4>First performed around 1596, Shakespeare's <i>A Midsummer Night's Dream</i> traces the escapades of four Athenians who retreat to the forest only to find themselves bewitched by supernatural forces.</h4>
</center>

<hr>
<br>
<br>
<center>
<b>Synopsis<br></b>
Provides relevant insight into the world of the text to provide a foundation for the argument to come (thesis)
</center>
<br>
<center>
<b>Focus<br>
</b></center>
<center>
A transitional sentence or two that places a "viewfinder" on the broader text and defines the area of interest that you intend to discuss in the essay.
<br>
What's a viewfinder? The camera component that shows the photographer the area of the subject that will be included in a photograph.
</center>
<br>
<center>
<b>Thesis<br></b></center>
<center>
1. Makes an argumentative assertion<br>
2. Provides a roadmap for how you will prove your claim<br>
</center>

<br>

<br>